A look into Kamala Harris' polls in the upcoming 2024 US Presidential Election 

### 2024-11-03 paper/paper.qmd
Updated Data and references files

@@

# Methodology

>>>>

```{r}
#| include: true
#| warning: false
#| message: false

@@

just_harris_high_quality <-
  read_csv(file = here::here("data/02-analysis_data/harris.csv"))

#### Plot data ####
base_plot <- ggplot(just_harris_high_quality, aes(x = end_date, y = pct)) +
  theme_classic() +
  labs(y = "Harris percent", x = "Date")

# Plots poll estimates and overall smoothing
base_plot +
  geom_point() +
  geom_smooth()

# Color by pollster
# This gets messy - need to add a filter - see line 21
base_plot +
  geom_point(aes(color = pollster)) +
  geom_smooth() +
  theme(legend.position = "bottom")

# Facet by pollster
# Make the line 21 issue obvious
# Also - is there duplication???? Need to go back and check
base_plot +
  geom_point() +
  geom_smooth() +
  facet_wrap(vars(pollster))

# Color by pollscore
base_plot +
  geom_point(aes(color = factor(pollscore))) +
  geom_smooth() +
  theme(legend.position = "bottom")

# Measurement
